\abstract{
    Mathematical models are a gateway into both theoretical and experimental understanding. However, sometimes these models need certain parameters to be established in order to obtain the optimal behaviour or value. This is done by using an optimization method that obtains certain parameters for optimal behaviour that may be a minimum (or maximum) result. Global optimization is a branch of optimization that takes a model and determines the global minimum for a given domain.
    However, global optimizations can become extremely challenging when the domain yields multiple local minima. Moreover, the complexity of the mathematical model and the consequent lengths of calculations tend to increase the amount of time required for the solver to find the solution.
    To address these challenges, two pieces of software were developed that aided the solver in optimizing a black box problem. The first piece of software developed is called Computefarm, a distributed system that parallelizes the iteration step of a solver by distributing function evaluations to idle computers. The second piece of software is an Optimization Database that is used to monitor the function and to store extra information on functions and results. It is also used to prevents data from being lost due to an optimization failure. 

    In this thesis, both Computefarm and the Optimization Database are used in the context of two particular applications. The first is designing quantum error correction circuits. Quantum computers cannot rely on software to correct errors because of the quantum mechanical properties that allow non-deterministic behaviour in the quantum bit. This means the quantum bits can change states between $(0,1)$ at any point in time. There are various ways to stabilize the quantum bits; however,
    errors in the system of quantum bits and the system to measure the states can occur. Therefore, error correction circuits are designed to correct for these different types of errors to ensure a high fidelity of the overall circuit. A simulation of a quantum error correction circuit is used to determine the properties of components needed to stabilize for minimal error. This design is optimized with the use of the Optimization Database and Computefarm to obtain the properties needed to achieve a low error rate. 
    The second application is crystal structure prediction, in which the total energy of crystal lattice is minimized to obtain its stability. Stable structures of carbon and silicon dioxide are obtained by using Computefarm and the Optimization Database. These software packages establish and store various stable structures and post-processing data for classification of the structure. The database is then used to obtain most stable structures of carbon and silicon dioxide for further research.
}
